Ensuring Fairness with Transparent Auditing of Quantitative Bias in AI Systems\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-04-26 abstract.tex
Slight change

\section{Introduction}
In recent years, the accelerating pace of artificial intelligence (AI) technologies have revolutionized numerous fields. In healthcare, AI-driven diagnostic systems streamline disease identification, while in finance, automated trading algorithms analyze market trends to execute optimal trades swiftly. This remarkable progress has reached diverse industries,sprouting out various applications for different purposes.

@@

Cases such as COMPAS underscore the critical importance of rigorously examining the fairness of AI systems by third parties. Fairness is fundementally a subjective social construct, heavily influenced by cultural context and deeply rooted in historical inequalities.

We leverage quantitative measures that provide transparent and objective insights. By employing mathematically rigorous methodologies, our research can offer a more deeper look into the fairness of AI systems, enabling third parties to make more informed and robust judgment. For example, it would reveal that the COMPAS system violates a fairness measure called equalized odds.

>>>>

\begin{IEEEkeywords}
AI, fairness, auditing
\end{IEEEkeywords}

\section{Introduction}
In recent years, the accelerating pace of artificial intelligence (AI) technologies have revolutionized numerous fields. In healthcare, AI-driven diagnostic systems streamline disease identification, while in finance, automated trading algorithms analyze market trends to execute optimal trades swiftly. This remarkable progress has reached diverse industries, sprouting out various applications for different purposes.

@@

Cases such as COMPAS underscore the critical importance of rigorously examining the fairness of AI systems by third parties. Fairness is fundementally a subjective social construct, heavily influenced by cultural context and deeply rooted in historical inequalities. However, there have been development in research leveraging statistical metrics to quantify fairness that provide transparent and objective insights.

By employing such mathematically rigorous methodologies, our research can offer a more deeper look into the fairness of AI systems, enabling third parties to make more informed and robust judgment. For example, it would reveal that the COMPAS system violates a fairness measure called equalized odds.
